A comparative risk assesment of U.S. regional active transport using the ITHIM model

### 2016-10-05 manuscript/manuscript.tex
Cleaned up manuscript a little

\newcommand{\col}[2][red]{\textcolor{#1}{#2}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\package}{\emph{ITHIM}}
\newcommand{\ithim}{\emph{ITHIM}}
\newcommand{\R}{\emph{R}}
\newcommand{\sgy}[1]{{\itshape\col{#1}}}
\newcommand{\XX}{\sgy{XX}}
\newcommand{\webpage}{\url{http://www.ithim.ghi.wisc.edu}}
\newcommand{\af}{\textrm{PAF}}
\newcommand{\mets}{MET-hrs./week}
\newcommand{\pEm}[1]{$\mathrm{PM}_{#1}$}
\newcommand{\vmt}{$\mathrm{VMT}$}
\newcommand{\logNormal}{log-normal}

@@

\begin{equation}
\af = \frac{\int R(x)P(x) dx  - \int R(x)Q(x) dx }{\int R(x)P(x) dx}
\end{equation}

Here $R(x)$ represents the risk when the individual has exposure $x$,
physical activity (\mets).  $P(x)$ and $Q(x)$ denote the population
density of individuals with exposure $x$, in the baseline and
alternate scenarios, respectively.  The exposure variable, $x$, is
modeled as the sum of two independent random variables, travel-related
exposure and non-travel-related exposure.  Non-travel-related exposure
is modeled with a \logNormal{} distribution with the age-sex specific
mean ratios for non-travel-related exposure are estimated from the
ATUS \cite{ATUS}.  The referent group mean is treated as a variable
and the coefficient of variation is treated as constant across age-sex
strata and estimated with ATUS.  We see in Figure \ref{dalyFigure}
that varying the mean values for non-travel-related exposure does not
greatly affect the estimate for disease burden.  The distribution for
travel-related exposure is estimated from the time spent walking or
cycling, i.e., active transport time, which as in the original ITHIM
model has a \logNormal{} distribution with constant coefficient of
variation across age-sex strata \cite{}.  Travel-related exposure
is estimated from active transport time using assumptions about how
much physical activity is required for cycling and walking.

>>>>

\newcommand{\col}[2][red]{\textcolor{#1}{#2}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\package}{\emph{ITHIM}}
\newcommand{\ithim}{\emph{ITHIM}}
\newcommand{\R}{\emph{R}}
\newcommand{\sgy}[1]{{\itshape\col{#1}}}
\newcommand{\XX}{\sgy{XX}}
\newcommand{\webpage}{\url{http://www.ithim.ghi.wisc.edu}}
\newcommand{\af}{\mathrm{PAF}}
\newcommand{\mets}{MET-hrs./week}
\newcommand{\pEm}[1]{$\mathrm{PM}_{#1}$}
\newcommand{\vmt}{$\mathrm{VMT}$}
\newcommand{\logNormal}{log-normal}

@@

\begin{equation}
\af = \frac{\int \! R(x)P(x) \, \mathrm{d}x  - \int \! R(x)Q(x) \, \mathrm{d}x}{\int \! R(x)P(x) \, \mathrm{d}x}
\end{equation}

Here $R(x)$ represents the risk when the individual has exposure $x$,
physical activity (\mets).  $P(x)$ and $Q(x)$ denote the population
density of individuals with exposure $x$, in the baseline and
alternate scenarios, respectively.  The exposure variable, $x$, is
modeled as the sum of two independent random variables, travel-related
exposure and non-travel-related exposure.  Non-travel-related exposure
is modeled with a \logNormal{} distribution with the age-sex specific
mean ratios for non-travel-related exposure are estimated from the
ATUS \cite{ATUS}.  The referent group mean is treated as a variable
and the coefficient of variation is treated as constant across age-sex
strata and estimated with ATUS.  We see in Figure \ref{dalyFigure}
that varying the mean values for non-travel-related exposure does not
greatly affect the estimate for disease burden.  The distribution for
travel-related exposure is estimated from the time spent walking or
cycling, i.e., active transport time, which as in the original ITHIM
model has a \logNormal{} distribution with constant coefficient of
variation across age-sex strata.  Travel-related exposure is estimated
from active transport time using assumptions about how much physical
activity is required for cycling and walking.
